---
title: "Untitled"
author: "Ania"
date: "17/02/2022"
output: html_document
---

Loading libraries
```{r, echo= = FALSE}
library(rlang)
library(readxl)
library(writexl)
library(dplyr)
library(stringr)
library(tidyverse)
library(ggplot2)
library(hrbrthemes) # for heatmaps
library(magrittr)
library(pheatmap)
library(MixGHD) # hierarchical clustering which i will finally not use
library(viridis)
library(ggpubr)
library(hash)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1.Loading datasets

U133A:
```{r}
U133A <- read_excel("/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Downloaded_tables/HS_AFFY_U133A.xlsx")

U133A <-U133A[,-c(1,3,4,5)]
colnames(U133A) <- c("Perturbations", "FC:BM2","p-value:BM2",
                       "FC:HBD1","p-value:HBD1",  #DEFB1
                       "FC:HBD2","p-value:HBD2",  # DEFB4A
                       "FC:LL37","p-value:LL37",
                       "FC:REG3A","p-value:REG3A",
                       "FC:PLA2G2A","p-value:PLA2G2A",
                       "FC:PGLYRP1","p-value:PGLYRP1",
                       "FC:PGLYRP4","p-value:PGLYRP4",
                       "FC:IL1B","p-value:IL1B",
                       "FC:IL8","p-value:IL8",
                       "FC:CCL20","p-value:CCL20",
                       "FC:TNF","p-value:TNF" )

U133A <- U133A[4:nrow(U133A),]
U133A_modified <-data.frame(lapply(U133A,as.numeric))
U133A_modified$Perturbations <- U133A$Perturbations
dim(U133A_modified)

Pert_names_before_U133 <-U133A_modified$Perturbations #keep pertubrations column, keep names only!

Pert_names_after_U133<-c()
for (i in 1:length(Pert_names_before_U133)) {
  Pert_names_after_U133[i] <- str_extract(Pert_names_before_U133[i], "([^\\s]+)") 
}

U133A_modified <-U133A_modified[ , grepl( "FC." , names(U133A_modified) ) ]

U133A_modified <-cbind(as.data.frame(Pert_names_after_U133),as.data.frame(Pert_names_before_U133), U133A_modified)

colnames(U133A_modified) <- c("Compounds", "Original","BM2", "HBD1","HBD2", "LL37", "REG3A", "PLA2G2A","PGLYRP1","PGLYRP4", "IL1B", "IL8", "CCL20", "TNF")

```
```{r}

#write_xlsx(U133A_modified,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/U133A_all_compounds.xlsx")
```

U133APLUS:

```{r}
U133A_PLUS <- read_excel("/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Downloaded_tables/HS_AFFY_U133PLUS_2.xlsx")

U133A_PLUS <-U133A_PLUS[,-c(1,3,4,5)]
colnames(U133A_PLUS) <- c("Perturbations", 
                       "FC:BM2","p-value:BM2",
                       "FC:HBD1","p-value:HBD1",  #DEFB1
                       "FC:HBD2","p-value:HBD2",  # DEFB4A
                       "FC:HBD3","p-value:HBD3",
                       "FC:HBD4","p-value:HBD4",
                       "FC:LL37","p-value:LL37",
                       "FC:REG3A","p-value:REG3A",
                       "FC:PLA2G2A","p-value:PLA2G2A",
                       "FC:PGLYRP1","p-value:PGLYRP1",
                       "FC:PGLYRP2","p-value:PGLYRP2",
                       "FC:PGLYRP3","p-value:PGLYRP3",
                       "FC:PGLYRP4","p-value:PGLYRP4",
                       "FC:IL1B","p-value:IL1B",
                       "FC:IL8","p-value:IL8",
                       "FC:CCL20","p-value:CCL20",
                       "FC:TNF","p-value:TNF" )

U133A_PLUS <- U133A_PLUS[4:nrow(U133A_PLUS),]
U133APLUS_modified <-data.frame(lapply(U133A_PLUS,as.numeric))
U133APLUS_modified$Perturbations <- U133A_PLUS$Perturbations
dim(U133APLUS_modified)

Pert_names_before_U133PLUS <-U133APLUS_modified$Perturbations #keep pertubrations column, keep names only!

Pert_names_after_U133PLUS<-c()
for (i in 1:length(Pert_names_before_U133PLUS)) {
  Pert_names_after_U133PLUS[i] <- str_extract(Pert_names_before_U133PLUS[i], "([^\\s]+)") 
}

U133APLUS_modified <-U133APLUS_modified[, grepl("FC.",names(U133APLUS_modified)) ]

U133APLUS_modified <-cbind(as.data.frame(Pert_names_after_U133PLUS),as.data.frame(Pert_names_before_U133PLUS), U133APLUS_modified)

colnames(U133APLUS_modified) <- c("Compounds", "Original","BM2", "HBD1","HBD2","HBD3","HBD4", "LL37", "REG3A", "PLA2G2A","PGLYRP1","PGLYRP2","PGLYRP3","PGLYRP4", "IL1B", "IL8", "CCL20", "TNF")

```

```{r}

#write_xlsx(U133APLUS_modified,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/U133APLUS_all_compounds.xlsx")
```


U219:
```{r}
U219 <- read_excel("/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Downloaded_tables/HS_AFFY_U219.xlsx")

U219 <-U219[,-c(1,3,4,5)]
colnames(U219) <- c("Perturbations", 
                       "FC:BM2","p-value:BM2",
                       "FC:HBD1","p-value:HBD1",  #DEFB1
                       "FC:LL37","p-value:LL37",
                       "FC:REG3A","p-value:REG3A",
                       "FC:PLA2G2A","p-value:PLA2G2A",
                       "FC:PGLYRP1","p-value:PGLYRP1",
                       "FC:PGLYRP2","p-value:PGLYRP2",
                       "FC:PGLYRP3","p-value:PGLYRP3",
                       "FC:PGLYRP4","p-value:PGLYRP4",
                       "FC:IL1B","p-value:IL1B",
                       "FC:IL8","p-value:IL8",
                       "FC:CCL20","p-value:CCL20",
                       "FC:TNF","p-value:TNF" )

U219 <- U219[4:nrow(U219),]
U219_modified <-data.frame(lapply(U219,as.numeric))
U219_modified$Perturbations <- U219$Perturbations
dim(U219_modified)

Pert_names_before_U219 <-U219_modified$Perturbations #keep pertubrations column, keep names only!

Pert_names_after_U219<-c()
for (i in 1:length(Pert_names_before_U219)) {
  Pert_names_after_U219[i] <- str_extract(Pert_names_before_U219[i], "([^\\s]+)") 
}

U219_modified <-U219_modified[, grepl("FC.",names(U219_modified)) ]

U219_modified <-cbind(as.data.frame(Pert_names_after_U219),as.data.frame(Pert_names_before_U219), U219_modified)

colnames(U219_modified) <- c("Compounds", "Original","BM2", "HBD1", "LL37", "REG3A", "PLA2G2A","PGLYRP1","PGLYRP2","PGLYRP3","PGLYRP4", "IL1B", "IL8", "CCL20", "TNF")
```

```{r}

#write_xlsx(U219_modified,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/U219_all_compounds.xlsx")
```


LINC-L1000
```{r}
LINC <- read_excel("/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Downloaded_tables/HS_LINC_L1000.xlsx")

LINC <-LINC[,-c(1,3,4,5)]
colnames(LINC) <- c("Perturbations", 
                       "FC:BM2","p-value:BM2",
                       "FC:HBD1","p-value:HBD1", #DEFB1
                       "FC:HBD2","p-value:HBD2", #DEFB4A
                       "FC:LL37","p-value:LL37",
                       "FC:REG3A","p-value:REG3A",
                       "FC:PLA2G2A","p-value:PLA2G2A",
                       "FC:PGLYRP1","p-value:PGLYRP1",
                       "FC:PGLYRP4","p-value:PGLYRP4",
                       "FC:IL1B","p-value:IL1B",
                       "FC:IL8","p-value:IL8",
                       "FC:CCL20","p-value:CCL20",
                       "FC:TNF","p-value:TNF" )

LINC <- LINC[4:nrow(LINC),]
LINC_modified <-data.frame(lapply(LINC,as.numeric))
LINC_modified$Perturbations <- LINC$Perturbations
dim(LINC_modified)

Pert_names_before_LINC <-LINC_modified$Perturbations #keep pertubrations column, keep names only!

Pert_names_after_LINC<-c()
for (i in 1:length(Pert_names_before_LINC)) {
  Pert_names_after_LINC[i] <- str_extract(Pert_names_before_LINC[i], "([^\\s]+)") 
}

LINC_modified <-LINC_modified[, grepl("FC.",names(LINC_modified)) ]

LINC_modified <-cbind(as.data.frame(Pert_names_after_LINC),as.data.frame(Pert_names_before_LINC), LINC_modified)

colnames(LINC_modified) <- c("Compounds", "Original","BM2", "HBD1","HBD2", "LL37", "REG3A", "PLA2G2A","PGLYRP1","PGLYRP4", "IL1B", "IL8", "CCL20", "TNF")

```

```{r}
#write_xlsx(LINC_modified,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/LINC_all_compounds.xlsx")
```

So datasets I've got:
```{r}

U133A_modified  #"BM2","HBD1","HBD2","LL37","REG3A","PLA2G2A","PGLYRP1","PGLYRP4",   "IL1B","IL8","CCL20","TNF"

U133APLUS_modified #"BM2","HBD1","HBD2","HBD3","HBD4","LL37","REG3A","PLA2G2A","PGLYRP1","PGLYRP2","PGLYRP3","PGLYRP4","IL1B","IL8","CCL20","TNF" 

U219_modified #"BM2","HBD1","LL37","REG3A","PLA2G2A","PGLYRP1","PGLYRP2","PGLYRP3",   "PGLYRP4","IL1B","IL8","CCL20","TNF" 

LINC_modified #"BM2","HBD1","HBD2","LL37","REG3A","PLA2G2A","PGLYRP1","PGLYRP4","IL1B","IL8","CCL20","TNF"
```

#2. Find the compounds inducing the highest gene expression for each dataset 
Separate dataset for each platform into separate tables for each gene, do the analysis of each gene to identify compounds that can be interesting!!

```{r function to use}
find_expression <- function(data, gene){
  
  ordered_data <- data %>%
  dplyr::filter(!!rlang::parse_expr(gene) >= 2) %>% 
  dplyr::select(c(Compounds, Original, gene, IL1B,IL8, CCL20,TNF)) %>%
  arrange(desc(!!rlang::parse_expr(gene)))

  return(ordered_data)
} 
```

U133A_modified
```{r}
#HBD1

U133A_HBD1 <- U133A_modified %>%
  arrange(desc(U133A_modified$HBD1)) %>%
  filter(HBD1 >= 2)

U133A_HBD1 <- U133A_HBD1[,c("Compounds","Original","HBD1","IL1B","IL8", "CCL20", "TNF")]

#HBD2

U133A_HBD2 <- find_expression(U133A_modified,"HBD2")

#write.csv(U133A_HBD2,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133A_HBD2.csv")

#LL37

U133A_LL37 <-find_expression(U133A_modified,"LL37")

#write.csv(U133A_LL37,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133A_LL37.csv")

#REG3A

U133A_REG3A <- find_expression(U133A_modified,"REG3A")

#PLA2G2A

U133A_PLA2G2A <- find_expression(U133A_modified,"PLA2G2A")

#write.csv(U133A_PLA2G2A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133A_PLA2G2A.csv")

#PGLYRP1

U133A_PGLYRP1 <- find_expression(U133A_modified,"PGLYRP1")

#write.csv(U133A_PGLYRP1,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133A_PGLYRP1.csv")


#PGLYRP4

U133A_PGLYRP4 <- find_expression(U133A_modified,"PGLYRP4")

#write.csv(U133A_PGLYRP4,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133A_PGLYRP4.csv")
```

U133APLUS_modified
```{r}
#"HBD1

U133APLUS_HBD1 <- find_expression(U133APLUS_modified,"HBD1")

#write.csv(U133APLUS_HBD1,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_HBD1.csv")

#HBD2

U133APLUS_HBD2 <- find_expression(U133APLUS_modified,"HBD2")

#write.csv(U133APLUS_HBD2,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_HBD2.csv")

#HBD3

U133APLUS_HBD3 <- find_expression(U133APLUS_modified,"HBD3")

#write.csv(U133APLUS_HBD3,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_HBD3.csv")

#HBD4

U133APLUS_HBD4 <- find_expression(U133APLUS_modified,"HBD4")

#write.csv(U133APLUS_HBD4,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_HBD4.csv")

#LL37

U133APLUS_LL37 <- find_expression(U133APLUS_modified,"LL37")

#write.csv(U133APLUS_LL37,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_LL37.csv")

#REG3A

U133APLUS_REG3A <- find_expression(U133APLUS_modified,"REG3A")

#write.csv(U133APLUS_REG3A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_REG3A.csv")

#PLA2G2A 

U133APLUS_PLA2G2A <- find_expression(U133APLUS_modified,"PLA2G2A")

#write.csv(U133APLUS_PLA2G2A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_PLA2G2A.csv")

#PGLYRP1

U133APLUS_PGLYRP1 <- U133APLUS_modified %>%
  arrange(desc(U133APLUS_modified$PGLYRP1)) %>%
  filter(PGLYRP1 >= 2)

U133APLUS_PGLYRP1 <- U133APLUS_PGLYRP1[,c("Compounds","Original","PGLYRP1","IL1B","IL8", "CCL20", "TNF")]

#PGLYRP2

U133APLUS_PGLYRP2 <-find_expression(U133APLUS_modified,"PGLYRP2")

#write.csv(U133APLUS_PGLYRP2,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_PGLYRP2.csv")

#PGLYRP3

U133APLUS_PGLYRP3 <-find_expression(U133APLUS_modified,"PGLYRP3")

#PGLYRP4

U133APLUS_PGLYRP4 <-  find_expression(U133APLUS_modified,"PGLYRP4")

#write.csv(U133APLUS_PGLYRP4,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/U133APLUS_PGLYRP4.csv")

```

U219_modified (not a single gene)
```{r}
#HBD1
find_expression(U219_modified, "HBD1")

#LL37
find_expression(U219_modified, "LL37")

#REG3A
find_expression(U219_modified, "REG3A")

#PLA2G2A
find_expression(U219_modified, "PLA2G2A")

#PGLYRP1
find_expression(U219_modified, "PGLYRP1")

#PGLYRP2
find_expression(U219_modified, "PGLYRP2")

#PGLYRP3
find_expression(U219_modified, "PGLYRP3")

#PGLYRP4
find_expression(U219_modified, "PGLYRP4")
```

LINC_modified
```{r}

#HBD1

LINC_HBD1 <- find_expression(LINC_modified, "HBD1")

#write.csv(LINC_HBD1,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/LINC_HBD1.csv")

unique_LINC_HBD1 <- LINC_HBD1[!duplicated(LINC_HBD1$Compounds),]

#write.csv(unique_LINC_HBD1,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/unique_LINC_HBD1.csv")

#HBD2

LINC_HBD2 <- find_expression(LINC_modified, "HBD2")

#write.csv(LINC_HBD2,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/LINC_HBD2.csv")

unique_LINC_HBD2 <- LINC_HBD2[!duplicated(LINC_HBD2$Compounds),]

#write.csv(unique_LINC_HBD2,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/unique_LINC_HBD2.csv")

#LL37

LINC_LL37 <- find_expression(LINC_modified, "LL37")

#write.csv(LINC_LL37,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/LINC_LL37.csv")

unique_LINC_LL37 <- LINC_LL37[!duplicated(LINC_LL37$Compounds),]

#write.csv(unique_LINC_LL37,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/unique_LINC_LL37.csv")

#REG3A

LINC_REG3A <- find_expression(LINC_modified, "REG3A")

#write.csv(LINC_REG3A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/LINC_REG3A.csv")

unique_LINC_REG3A <- LINC_REG3A[!duplicated(LINC_REG3A$Compounds),]

#write.csv(unique_LINC_REG3A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/unique_LINC_REG3A.csv")

#PLA2G2A

LINC_PLA2G2A <- find_expression(LINC_modified, "PLA2G2A")

#write.csv(LINC_PLA2G2A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/LINC_PLA2G2A.csv")

unique_LINC_PLA2G2A <- LINC_PLA2G2A[!duplicated(LINC_PLA2G2A$Compounds),]

#write.csv(unique_LINC_PLA2G2A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/unique_LINC_PLA2G2A.csv")

#PGLYRP1

LINC_PGLYRP1 <- find_expression(LINC_modified, "PGLYRP1")

#write.csv(LINC_PGLYRP1,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/LINC_PGLYRP1.csv")

unique_LINC_PGLYRP1 <- LINC_PGLYRP1[!duplicated(LINC_PGLYRP1$Compounds),]

#write.csv(unique_LINC_PGLYRP1,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/unique_LINC_PGLYRP1.csv")

#PGLYRP4

LINC_PGLYRP4 <- find_expression(LINC_modified, "PGLYRP4")

#write.csv(LINC_PGLYRP4,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/LINC_PGLYRP4.csv")

unique_LINC_PGLYRP4 <- LINC_PGLYRP4[!duplicated(LINC_PGLYRP4$Compounds),]

#write.csv(unique_LINC_PGLYRP4,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/output_tables_for_excel/unique_LINC_PGLYRP4.csv")


```


#3.Analysis of LINC compounds in HT-29 cell type. 

```{r}

LINC_perturbations <- LINC_modified$Original
  
LINC_time <- c()
LINC_conc <- c()
LINC_cell <- c()
LINC_compound <- c()

for (i in 1:length(LINC_perturbations)){

  linc_perturbations_results <- str_match(as.list(LINC_perturbations[i]), ".+\\((.+)\\;\\s?(.+)\\;\\s?(.+)\\).*\\(.*")
  LINC_time[i] <- linc_perturbations_results[2]
  LINC_conc[i] <- linc_perturbations_results[3]
  LINC_cell[i] <- linc_perturbations_results[4]
  LINC_compound[i] <-str_extract(LINC_perturbations[i], "([^\\s]+)") 
  
}

LINC_compounds <-cbind(as.data.frame(LINC_cell),as.data.frame(LINC_conc),as.data.frame(LINC_time), as.data.frame(LINC_modified))

LINC_compounds_HT29 <-LINC_compounds %>%
  filter(LINC_cell == "HT29") 

LINC_HT29_f_gathered <- gather(LINC_compounds_HT29,key = Gene, value = Expression_ratio, -c(1:5)) 

HT29_freq_each_gene <-LINC_HT29_f_gathered %>%
  filter(Gene %in% AMP_LINC) %>%
  group_by(Compounds,Gene) %>%
  summarise(Gene_Frequency = sum((Expression_ratio >= 2) == TRUE)) %>%
  pivot_wider(names_from = Gene,values_from = Gene_Frequency)

# write_xlsx(HT29_freq_each_gene,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/HT29_freq_each_gene.xlsx")

## Get names of upregulated genes for each compound in HT-29 cells. and then adding it to google docs, gonna add it manually this time!

colnames(HT29_freq_each_gene)
HT29_freq_each_gene[,2:ncol(HT29_freq_each_gene)]

HT29_logic <- as.data.frame(HT29_freq_each_gene[,AMP_LINC] >= 1)

HT29_genes_concatenated <- list()
for (i in 1:nrow(HT29_logic)) {
  numberss <- which(HT29_logic[i,] == TRUE)
  HT29_genes_concatenated[[i]] <- AMP_LINC[numberss]
}

names(HT29_genes_concatenated) <- HT29_freq_each_gene$Compounds
nm_HT29 <- names(HT29_genes_concatenated)
result_HT29 <- lapply(unique(nm_HT29), function(n) unname(unlist(HT29_genes_concatenated[nm_HT29 %in% n])))
names(result_HT29) <- unique(nm_HT29)
result_HT29 <-lapply(result_HT29, function(x) toString(unique(x)))
result_HT29 <-as.data.frame(unlist(result_HT29))
result_HT29$Compounds <- unique(HT29_freq_each_gene$Compounds)

# write_xlsx(result_HT29, "/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/listed_upregulated_genes_HT29.xlsx")

as.data.frame(table(LINC_compounds_HT29$Compounds))
#Compounds were tested either 5 or 6 times
as.data.frame(table(LINC_compounds_HT29$LINC_conc))
as.data.frame(table(LINC_compounds_HT29$LINC_time))

```

This bit was about creating the drug_main_analaysis (or sth like that). Before I only had info about one AMP gene and PRo genes,  here I include info about expression of other genes in this condition.
```{r}
#sunitinib (24h; 1.11uM; HA1E) / DMSO control (24h; HA1E)
main_analysis_of_compounds[206,2] <- "sunitinib (24h; 1.11uM; HA1E) / DMSO control (24h; HA1E)" #somehow I deleted this value

LINC_selected_all_genes_to_add <- LINC_modified[LINC_modified$Original %in% main_analysis_of_compounds$Original,]

U133A_selected_all_genes_to_add <- U133A_modified[U133A_modified$Original %in% main_analysis_of_compounds$Original, ]

U133APLUS_selected_all_genes_to_add <- U133APLUS_modified[U133APLUS_modified$Original %in%  main_analysis_of_compounds$Original,]

nrow(LINC_selected_all_genes_to_add) #270
nrow(U133A_selected_all_genes_to_add) #28
nrow(U133APLUS_selected_all_genes_to_add) # 21
# that doesn't add up to 321, it's 319. Okay that's bc there are duplicates it seems! # geldanamycin, captopril, SC-58125

which(duplicated(main_analysis_of_compounds$Compounds))
which(duplicated(main_analysis_of_compounds$Original)) #276 309
# even duplicated annotations, that's fine! it happens :) and at least now I got rid of it :)

attempt_main_analysis <- main_analysis_of_compounds[,-c(3:7)]
attempt_with_LINC <-full_join(attempt_main_analysis,LINC_selected_all_genes_to_add, by = "Original" ) # good, we can leave it here since that's the trickiest one
attempt_with_LINC <-attempt_with_LINC[,-6]


#write_xlsx(attempt_with_LINC, "/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/attempt_with_LINC.xlsx")
```

#4. Adding information about what AMPs were upregulated for each compound

The idea is to add a new column to the main analysis table (~317 compounds) where it'll say what AMPs were induced for this compound. 

-it would be one row/copmpound with all AMPs listed maybe in the descending order!

Loading datasets I will use 
```{r}
#data with the individual compounds
main_analysis_of_compounds$`Compounds (blue = approved, purple = clinical trial or discontinued, white = non)` # line 608

#platforms
U133A_modified # chunk starting at 76
U133APLUS_modified # chunk starting at 33
LINC_modified # chunk starting at 170
```

Select rows that are in these conditions, for each platform
```{r}

#Error in stri_detect_regex(string, pattern, negate = negate, opts_regex = opts(pattern)) : Syntax error in regex pattern. (U_REGEX_RULE_SYNTAX, context=`(+)-JQ1`)
which(str_detect(string = main_analysis_of_compounds$Compounds, "\\(\\+\\)\\-"))
which(str_detect(string = main_analysis_of_compounds$Compounds, "\\(\\-\\)\\-"))
main_analysis_of_compounds[74,2] <- "minus_JQ1"
main_analysis_of_compounds[92,2] <- "plus_JQ1"
U133A_modified[107,1] <- "plus_isoprenaline"
U133A_modified[171,1] <- "minus_isoprenaline"
U133A_modified[1109,1] <- "catechin"
U133A_modified[1381,1] <- "chelidonine"

empty_string <- c()

for (i in 1:nrow(U133A_modified)){
  for (j in 1:nrow(main_analysis_of_compounds)){
    if(str_detect(string = main_analysis_of_compounds[j,2],pattern = U133A_modified[i,1]) == TRUE){
      empty_string <- c(empty_string, U133A_modified[i,1])
      break
    }
  }
}

empty_string_unique <- unique(empty_string) # 48

U133A_for_genes <-U133A_modified[U133A_modified$Compounds %in% empty_string_unique,]


str_detect(string = main_analysis_of_compounds[315,2],U133A_modified[1583,1])
# cobalt in cobalt chloride

```

Utlimate test of the approach above with LINC ( i should expect to have all compounds selected)
```{r}

LINC_modified$Compounds[which(LINC_modified$Compounds == "(+)-JQ1")] = "JQ1"
LINC_modified$Compounds[which(LINC_modified$Compounds == "(-)-JQ1")] = "JQ1"
LINC_modified$Compounds[which(LINC_modified$Compounds == "sutent")] = "sunitinib"
main_analysis_of_compounds[206,2] = "TGX-221"

 #that naming may be problematic. Better to change it 
empty_string_LINC <- c()

for (i in 1:nrow(LINC_modified)){
  for (j in 1:nrow(main_analysis_of_compounds)){
    if(str_detect(string = main_analysis_of_compounds[j,2],pattern = LINC_modified[i,1]) == TRUE){
      empty_string_LINC <- c(empty_string_LINC, LINC_modified[i,1])
      break
    }
  }
}

#okay we've got 21413! we've got it all!

empty_string_LINC <- unique(empty_string_LINC)


LINC_for_genes <-LINC_modified[LINC_modified$Compounds %in% empty_string_LINC,] # well yea, everything


```

```{r}
 #that naming may be problematic. Better to change it 
empty_string_U133APLUS <- c()

for (i in 1:nrow(U133APLUS_modified)){
  for (j in 1:nrow(main_analysis_of_compounds)){
    if(str_detect(string = main_analysis_of_compounds[j,2],pattern = U133APLUS_modified[i,1]) == TRUE){
      empty_string_U133APLUS <- c(empty_string_U133APLUS, U133APLUS_modified[i,1])  
      break
    }
  }
}

empty_string_U133APLUS <- unique(empty_string_U133APLUS)

U133APLUS_for_genes <-U133APLUS_modified[U133APLUS_modified$Compounds %in% empty_string_U133APLUS,] # 135 rows

# for some reason benzo[a]pyrene didn't work! makes no sense 
main_analysis_of_compounds[308,2]
U133APLUS_modified[19,1]
str_detect(string = main_analysis_of_compounds[308,2],pattern = U133APLUS_modified[19,1]) # 

```

Select compounds from main_analysis 
```{r}
#U133A

AMP_U133A_2 <- c("HBD1","HBD2","LL37","REG3A","PLA2G2A","PGLYRP1","PGLYRP4")

#get the frequency for each 
U133A_gathered <- U133A_for_genes %>%
  dplyr::select(1:10) %>%
  gather(key = Gene, value = Expression_ratio, -c(1:2)) 

U133A_freq_each_gene <-U133A_gathered %>%
  filter(Gene %in% AMP_U133A_2) %>%
  group_by(Compounds,Gene) %>%
  summarise(Gene_Frequency = sum((Expression_ratio >= 2) == TRUE)) %>%
  pivot_wider(names_from = Gene,values_from = Gene_Frequency)

write_xlsx(U133A_freq_each_gene,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/U133A_freq_each_gene.xlsx")

#the awful way i used to get the names, fine let's leave it for the moment
U133A_logic <- as.data.frame(U133A_for_genes[,AMP_U133A_2] > 2)
U133A_genes_concatenated <- list()
for (i in 1:nrow(U133A_logic)) {
  numberss <- which(U133A_logic[i,] == TRUE)
  U133A_genes_concatenated[[i]] <- AMP_U133A_2[numberss]
  
}
names(U133A_genes_concatenated) <- U133A_for_genes$Compounds
nm <- names(U133A_genes_concatenated)
result <- lapply(unique(nm), function(n) unname(unlist(U133A_genes_concatenated[nm %in% n])))
names(result) <- unique(nm)
result_U133A <-lapply(result, function(x) toString(unique(x)))
result_U133A <-as.data.frame(unlist(result_U133A))
result_U133A$Compounds <- unique(U133A_for_genes$Compounds)

write_xlsx(result_U133A,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/U133A_expressed_genes_each_compound.xlsx")


#U133APLUS
AMP_U133PLUS_2_0 <-c("HBD1","HBD2","HBD3","HBD4","LL37","REG3A","PLA2G2A","PGLYRP1","PGLYRP2","PGLYRP3","PGLYRP4" )

#get the frequency for each 
U133APLUS_gathered <- U133APLUS_for_genes %>%
  dplyr::select(1:14) %>%
  gather(key = Gene, value = Expression_ratio, -c(1:2)) 

U133APLUS_freq_each_gene <-U133APLUS_gathered %>%
  filter(Gene %in% AMP_U133PLUS_2_0) %>%
  group_by(Compounds,Gene) %>%
  summarise(Gene_Frequency = sum((Expression_ratio >= 2) == TRUE)) %>%
  pivot_wider(names_from = Gene,values_from = Gene_Frequency)

write_xlsx(U133APLUS_freq_each_gene,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/U133APLUS_freq_each_gene.xlsx")

#the (convvvvvoluted) way to get names of genes
U133APLUS_logic <- as.data.frame(U133APLUS_for_genes[,AMP_U133PLUS_2_0] > 2)

U133APLUS_genes_concatenated <- list()
for (i in 1:nrow(U133APLUS_logic)) {
  numberss <- which(U133APLUS_logic[i,] == TRUE)
  U133APLUS_genes_concatenated[[i]] <- AMP_U133PLUS_2_0[numberss]
  
}

names(U133APLUS_genes_concatenated) <- U133APLUS_for_genes$Compounds
nm_PLUS <- names(U133APLUS_genes_concatenated)
result_PLUS <- lapply(unique(nm_PLUS), function(n) unname(unlist(U133APLUS_genes_concatenated[nm_PLUS %in% n])))
names(result_PLUS) <- unique(nm_PLUS)
result_U133APLUS <-lapply(result_PLUS, function(x) toString(unique(x)))
result_U133APLUS <-as.data.frame(unlist(result_U133APLUS))
result_U133APLUS$Compounds <- unique(U133APLUS_for_genes$Compounds)

# write_xlsx(result_U133APLUS,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/U133APLUS_expressed_genes_each_compound.xlsx")

#LINC
AMP_LINC <- c("HBD1","HBD2","LL37","REG3A","PLA2G2A","PGLYRP1","PGLYRP4")

#get the frequency for each 
LINC_gathered <- LINC_for_genes %>%
  gather(key = Gene, value = Expression_ratio, -c(1:2)) 

LINC_freq_each_gene <-LINC_gathered %>%
  filter(Gene %in% AMP_LINC) %>%
  group_by(Compounds,Gene) %>%
  summarise(Gene_Frequency = sum((Expression_ratio >= 2) == TRUE)) %>%
  pivot_wider(names_from = Gene,values_from = Gene_Frequency)

# write_xlsx(LINC_freq_each_gene,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/LINC_freq_each_gene.xlsx")

LINC_logic <- as.data.frame(LINC_for_genes[,AMP_LINC] > 2)

LINC_genes_concatenated <- list()
for (i in 1:nrow(LINC_logic)) {
  numberss <- which(LINC_logic[i,] == TRUE)
  LINC_genes_concatenated[[i]] <- AMP_LINC[numberss]
}

names(LINC_genes_concatenated) <- LINC_for_genes$Compounds
nm_LINC <- names(LINC_genes_concatenated)
result_LINC <- lapply(unique(nm_LINC), function(n) unname(unlist(LINC_genes_concatenated[nm_LINC %in% n])))
names(result_LINC) <- unique(nm_LINC)
result_LINC <-lapply(result_LINC, function(x) toString(unique(x)))
result_LINC <-as.data.frame(unlist(result_LINC))
result_LINC$Compounds <- unique(LINC_for_genes$Compounds)

# they're all here but now i've got 268 compounds instead of 270. I think it's beacuse ive chagned sutent to sunetinib and (+)/(-)-JQ1 into JQ1
setdiff(unique(LINC_modified$Compounds),unique(LINC_for_genes$Compounds))

# write_xlsx(result_LINC,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/LINC_expressed_genes_each_compound.xlsx")

```

Okay so now it would be preferable to join these into one table and then join it with the compounds one, just wondering if it'd be possible really
``` {r}
drug_main_analysis <- read_xlsx("/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/drug_main_analysis_wip.xlsx")

result_U133APLUS
result_U133A
result_LINC

# write_xlsx(left_join(result_LINC,drug_main_analysis, by = "Compounds"),"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/drug_main_analysis_return_with_compounds_11_03_22.xlsx")

# i can actually leave it here, since they may repeat and I dont want to override them!

```

#5. Max and mean value for each gene for each compound
```{r}

#Find it for each platform

#U133A

 # I was a bit suprised with the choice of U133A_for_genes for this task. I forgot why I did that. The reason is that  platforms like U133A_modified and U133APLUS_modified contain even 1000s of unique compounds but I only want to find the max and median values of the compounds included in the main analysis.For LINC all compounds are included in HT29 cells simply because all compounds showed high expression at least once in the normal cells.

U133A_max_mean <- U133A_for_genes %>%
  gather(key = Gene, value = Expression_ratio, -c(1:2)) %>%
  group_by(Compounds,Gene) %>%
  summarise(Max = max(Expression_ratio),
            Median = median(Expression_ratio)) %>%
  pivot_wider(id_cols = Compounds, names_from = Gene, values_from = c(Max,Median)) %>%
  add_column(Max_HBD3 = NA,
             Max_HBD4 = NA,
             Max_PGLYRP2 = NA,
             Max_PGLYRP3 = NA,
             Median_HBD3 = NA,
             Median_HBD4 = NA,
             Median_PGLYRP2 = NA,
             Median_PGLYRP3 = NA)

#U133APLUS

U133APLUS_max_mean <-U133APLUS_for_genes %>%
  gather(key = Gene, value = Expression_ratio, -c(1:2)) %>%
  group_by(Compounds,Gene) %>%
  summarise(Max = max(Expression_ratio),
            Median = median(Expression_ratio)) %>%
  pivot_wider(id_cols = Compounds, names_from = Gene, values_from = c(Max,Median))

colnames(U133APLUS_max_mean)

#LINC

max_median_HT29_only <- LINC_HT29_f_gathered %>%
  # filter(Gene %in% AMP_LINC) %>%
  group_by(Compounds,Gene) %>%
  summarise(Max = max(Expression_ratio),
            Median = median(Expression_ratio)) %>%
  pivot_wider(id_cols = Compounds, names_from = Gene, values_from = c(Max,Median)) %>% add_column(Max_HBD3 = NA,
             Max_HBD4 = NA,
             Max_PGLYRP2 = NA,
             Max_PGLYRP3 = NA,
             Median_HBD3 = NA,
             Median_HBD4 = NA,
             Median_PGLYRP2 = NA,
             Median_PGLYRP3 = NA)


U133A_U133APLUS_LINC <-rbind(max_median_HT29_only, U133A_max_mean, U133APLUS_max_mean)
which(duplicated(U133A_U133APLUS_LINC$Compounds))
#nrow 347

# Okay now add these table, the issue is that the names won't match in some cases, but we just have to accept it

drug_main_analysis_18_03 <-read_xlsx("/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/Drug_main_analysis_18_03_22.xlsx")

##in drug_main_analysis_18_03, change names of compounds so they match with automatically selected names in U133A_U133APLUS_LINC e.g. valproic acid

# JQ1
which(drug_main_analysis_18_03$Compounds == "minus_JQ1")
drug_main_analysis_18_03[281,3] <- "JQ1"

#sodium chloride 

which(drug_main_analysis_18_03$Compounds == "sodium chloride") #309
drug_main_analysis_18_03[309,3] <- "sodium"

#polysinosici poly....

which(drug_main_analysis_18_03$Compounds == "polyinosinic-polycytidylic acid") #308
drug_main_analysis_18_03[308,3] <- "polyinosinic-polycytidylic"

#monastrol

which(drug_main_analysis_18_03$Compounds == "monastrol (drug?)") #315
drug_main_analysis_18_03[315,3] <- "monastrol"

#exisulind

which(drug_main_analysis_18_03$Compounds == "exisulind ((drug?))") #316
drug_main_analysis_18_03[316,3] <- "exisulind"

#cobalt chloride 

which(drug_main_analysis_18_03$Compounds == "cobalt chloride") #154
drug_main_analysis_18_03[154,3] <- "cobalt"

#benzopyrene

which(drug_main_analysis_18_03$Compounds == "benzo[a]pyrene") #148
drug_main_analysis_18_03 <- drug_main_analysis_18_03[-c(148), ]

#valproic acid

which(drug_main_analysis_18_03$Compounds == "valproic acid") #61
drug_main_analysis_18_03[61,3] <- "valproic"

#pirinixic acid

which(drug_main_analysis_18_03$Compounds == "pirinixic acid") #312
drug_main_analysis_18_03[312,3] <- "pirinixic"

drug_analysis_with_median_max<- left_join(x =  drug_main_analysis_18_03,y = U133A_U133APLUS_LINC, by= "Compounds")
#nrow of that is 339 instead of 316. Some compounds are duplicated. in the  U133A_U133APLUS_LINC table (where i joined the 3 tables, it was 347) but length(unqiue(drug_analysis_plus_LINC$Compounds)) is 316 so it should be fine!


#saving the main document with about 316 compounds where you can see toxicity profiles etc. 
write_xlsx(drug_analysis_with_median_max,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/ddrug_analysis_with_median_max18_03_22.xlsx")


#Now just load the most recent table from 

```

#6. I've got a list of top molecules, now I want to get rows when AMP DE is above 2. (chosen in excel)

```{r}

drug_analysis_with_median_max <- drug_analysis_with_median_max[,-c(7: 22)]

U133A_U133APLUS_platforms <- unique(drug_analysis_with_median_max$Platform)[2:length(unique(drug_analysis_with_median_max$Platform))] # basically save platform names that don't include LINC, that's because it's too many names at once

U133A_and_selected_compounds <- drug_analysis_with_median_max %>%
  filter(drug_analysis_with_median_max$Platform %in% U133A_U133APLUS_platforms)

#so I've got a table where for each gene, you have the max and median DE value. This was calculated based on all the experiments in which the compound was tested. Now, for each gene I want to see what are the highest MAX values above 2. I'm ordering it and then at the end I'll combine the tables for each gene and I'll calculate the frequency of each gene. In how many genes was the max value upregulated? I do it for LINC and U133A + U133APLUS separately as LINC has genrally much higher values!

find_expression_selected_genes <- function(data, gene){
  
  ordered_data <- data %>%
  arrange(desc(!!rlang::parse_expr(gene))) %>%
  dplyr::filter(!!rlang::parse_expr(gene) >= 2)

  return(ordered_data)
} 

HBD1_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_HBD1")

HBD2_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_HBD2")

HBD3_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_HBD3")

HBD4_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_HBD4")

LL37_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_LL37")

PGLYRP1_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_PGLYRP1")

PGLYRP2_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_PGLYRP2")

PGLYRP3_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_PGLYRP3")

PGLYRP4_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_PGLYRP4")

PLA2G2A_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_PLA2G2A")

REG3A_selected_U133A <-find_expression_selected_genes( U133A_and_selected_compounds,"Max_REG3A")

all_selected_compounds_U133A_U133APLUS <- rbind(HBD1_selected_U133A,HBD2_selected_U133A,HBD3_selected_U133A, HBD4_selected_U133A,LL37_selected_U133A, PGLYRP1_selected_U133A, PGLYRP2_selected_U133A,PGLYRP3_selected_U133A,PGLYRP4_selected_U133A,PLA2G2A_selected_U133A,REG3A_selected_U133A ) %>%
  group_by(Compounds) %>%
  mutate(Freq = table(Compounds)) %>%
  arrange(desc(Freq)) %>%
  distinct()

all_selected_compounds_U133A_U133APLUS <- all_selected_compounds_U133A_U133APLUS[!all_selected_compounds_U133A_U133APLUS$Status == "Toxic",]

table_with_all_conditions_selected_U133A <- U133A_modified[U133A_modified$Compounds %in% unique(all_selected_compounds_U133A_U133APLUS$Compounds),]

table_with_all_conditions_selected_U133APLUS <- U133APLUS_modified[U133APLUS_modified$Compounds %in% unique(all_selected_compounds_U133A_U133APLUS$Compounds),]

```

Repeat something similar for LINC. This time, look at the max, median values in HT29 cells, since they're available. Retain approved and clinical compounds within the first 30 rows (greatest AMP values).

```{r}
#LINC only, remember that here it's best to look at HT-29 cells only! So i'm gonna use max_median_HT29_only table instead of compounds from drug_analysis_with_median_max

LINC_containing_platforms <- c("LINC", "LINC & U133A","LINC & U133A & U133APLUS", "LINC & U133APLUS", "LINC & U133A & U219")

LINC_and_selected_compounds <- drug_analysis_with_median_max %>%
  filter(drug_analysis_with_median_max$Platform %in% LINC_containing_platforms)  ## drug_analysis_with_median_max contains results LINC results from HT29 already 

find_expression_selected_genes_for_LINC <- function(data, gene){
  
  ordered_data <- data %>%
  arrange(desc(!!rlang::parse_expr(gene))) %>%
  dplyr::filter(!!rlang::parse_expr(gene) >= 2)  
  
  ordered_data <- ordered_data[1:20,]
  ordered_data <- ordered_data[!is.na(ordered_data$Compounds),]
  
  return(ordered_data)
} 

HBD1_selected_LINC <-find_expression_selected_genes_for_LINC( LINC_and_selected_compounds,"Max_HBD1")

HBD2_selected_LINC <-find_expression_selected_genes_for_LINC( LINC_and_selected_compounds,"Max_HBD2")

LL37_selected_LINC <-find_expression_selected_genes_for_LINC( LINC_and_selected_compounds,"Max_LL37")

PGLYRP1_selected_LINC <-find_expression_selected_genes_for_LINC( LINC_and_selected_compounds,"Max_PGLYRP1")

PGLYRP4_selected_LINC <-find_expression_selected_genes_for_LINC( LINC_and_selected_compounds,"Max_PGLYRP4")

PLA2G2A_selected_LINC <-find_expression_selected_genes_for_LINC( LINC_and_selected_compounds,"Max_PLA2G2A")

REG3A_selected_LINC <-find_expression_selected_genes_for_LINC( LINC_and_selected_compounds,"Max_REG3A")

all_selected_compounds_LINC <- rbind(HBD1_selected_LINC,HBD2_selected_LINC,LL37_selected_LINC, PGLYRP1_selected_LINC,PGLYRP4_selected_LINC,PLA2G2A_selected_LINC,REG3A_selected_LINC) %>%
  group_by(Compounds) %>%
  mutate(Freq = table(Compounds)) %>%
  arrange(desc(Freq)) %>%
  distinct()

#the issue is now that I don't know which one is approved and which one isn't. 

## remove None,
all_selected_compounds_LINC <- all_selected_compounds_LINC[!all_selected_compounds_LINC$Status == "None",]

table_with_all_conditions_selected_LINC <- LINC_compounds_HT29[LINC_compounds_HT29$Compounds %in% unique(all_selected_compounds_LINC$Compounds),]

#table with initial DE values from experiments for all compounds from U133A, U133APLUS and LINC (not max and median values)

#repeat bc when re-run I've got an issue
table_with_all_conditions_selected_U133A <- U133A_modified[U133A_modified$Compounds %in% unique(all_selected_compounds_U133A_U133APLUS$Compounds),]

table_with_all_conditions_selected_U133APLUS <- U133APLUS_modified[U133APLUS_modified$Compounds %in% unique(all_selected_compounds_U133A_U133APLUS$Compounds),]

table_with_all_conditions_selected_U133A <- 
  table_with_all_conditions_selected_U133A %>%
  add_column(HBD3 = NA,
             HBD4 = NA,
             PGLYRP2 = NA,
             PGLYRP3 = NA,
             LINC_cell = NA,
             LINC_conc = NA,
             LINC_time = NA)

table_with_all_conditions_selected_LINC <- table_with_all_conditions_selected_LINC %>%
   add_column(HBD3 = NA,
             HBD4 = NA,
             PGLYRP2 = NA,
             PGLYRP3 = NA) 

table_with_all_conditions_selected_U133APLUS <- table_with_all_conditions_selected_U133APLUS %>%
  add_column(LINC_cell = NA,
             LINC_conc = NA,
             LINC_time = NA)

table_with_all_conditions_selected_LINC_U133A_andPLUS <- rbind(table_with_all_conditions_selected_U133A,table_with_all_conditions_selected_U133APLUS,table_with_all_conditions_selected_LINC)

write_xlsx(table_with_all_conditions_selected_LINC_U133A_andPLUS,"/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/table_with_all_conditions_selected_LINC_U133A_andPLUS.xlsx")
#22/03/22

#combine tables with max and median values too

selected_median_max <- rbind(all_selected_compounds_U133A, all_selected_compounds_LINC) # length(unique(selected_median_max$Compounds)) = 78
# selected_median_max <-selected_median_max[!duplicated(selected_median_max$Compounds),]

write_xlsx(selected_median_max, "/Users/Ania/Desktop/Szkoła/ENS /2nd_year/Stage/Practical/Genevestigator/Data_17_02_22_current/Work_in_progress_tables/selected_median_max.xlsx")

```
